---
title: "Batteries Bill Gao"
author: "JingjianGao"
date: "2023-04-26"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Main Question: How can Colorado address the challenge of balancing energy demands for its growing population and economy with the need for conservation and sustainability?

# Advances in technology and falling prices mean grid-scale battery facilities that can store increasingly large amounts of energy are enjoying record growth.

# The world’s largest battery energy storage system so far is the Moss Landing Energy Storage Facility in California, US, where the first 300-megawatt lithium-ion battery – comprising 4,500 stacked battery racks – became operational in January 2021.


## Initial Dataset import

```{r}
library(readxl)
library(dplyr)

battery_2020 <-read.csv("battery_2020.csv")

battery_2020_CO <- subset(battery_2020, State=="CO")

```

## EDA

```{r}
library(ggplot2)

#2016
write.csv(X3_4_Energy_Storage_Y2016, file="battery_2016.csv",row.names=FALSE)

battery_2016 <- read.csv("battery_2016.csv")

state_capacity2 <- battery_2016 %>%
  group_by(State) %>%
  summarize(Nameplate.Energy.Capacity..MWh. = sum(Nameplate.Energy.Capacity..MWh.))

# Plot the state capacity using ggplot2
ggplot(state_capacity2, aes(x = reorder(State,-Nameplate.Energy.Capacity..MWh.), y = Nameplate.Energy.Capacity..MWh.)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(aes(label = Nameplate.Energy.Capacity..MWh.), vjust = -0.5, size=2.5)+
  xlab("State") +
  ylab("Energy Capacity") +
  ggtitle("Total Energy Capacity by State in 2016")


# 2020

ggplot(data=battery_2020,aes(x=State,y=battery_2020$Nameplate.Energy.Capacity..MWh.,color=State))+
  geom_point()

# Sum up the capacity readings for each state using group_by and summarize
state_capacity <- battery_2020 %>%
  group_by(State) %>%
  summarize(Nameplate.Energy.Capacity..MWh. = sum(Nameplate.Energy.Capacity..MWh.))

# Plot the state capacity using ggplot2
ggplot(state_capacity, aes(x = reorder(State,-Nameplate.Energy.Capacity..MWh.), y = Nameplate.Energy.Capacity..MWh.)) +
  geom_bar(stat = "identity", fill = "skyblue") +
  geom_text(aes(label = Nameplate.Energy.Capacity..MWh.), vjust = -0.5, size=2.5)+
  xlab("State") +
  ylab("Energy Capacity") +
  ggtitle("Total Energy Capacity by State in 2020")

```

## Possible Models
```{r}
# Simple Linear Models

model1 <- lm(battery_2020$Nameplate.Energy.Capacity..MWh. ~ Technology+battery_2020$Nameplate.Reactive.Power.Rating+Operating.Month, data= battery_2020)

summary(model1)




```